Study of the hadronization of charged pions

### 2019-04-16 chap5.tex
Update all analysis figures

\begin{figure}[htb]
\centering
\includegraphics[width=7.4cm] {chap5-fig/a_RvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/a_RvZ.png} 
\includegraphics[width=7.4cm] {chap5-fig/a_PvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/a_PvNu.png} 
\caption {Results for multiplicity ratios (top) and the transverse momentum 
broadening (bottom) before applying any corrections.}
\label{fig:prelim}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
\caption {Preliminary results are compared with the acceptance corrected ones, 
for multiplicity ratios (top) and transverse momentum broadening 
(bottom). Only statistical errors are shown.}
\label{fig:AcceptPlots}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
\caption {Preliminary results are compared with the acceptance corrected ones, 
for multiplicity ratios (top) and transverse momentum broadening 
(bottom). Only statistical errors are shown.}
\label{fig:CCPlots}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {chap5-fig/b_RvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_RvZ.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvA.png} 
\includegraphics[width=7.4cm] {chap5-fig/b_PvQ2.png} 
\caption {Preliminary results including radiative corrections
compared to the ones without, 
for multiplicity ratios (top) and transverse momentum broadening 
(bottom). Only statistical errors are shown.}
\label{fig:RCPlots}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=8.5cm] {chap5-fig/c_RvA.png}
\caption {Multiplicity ratios as a function of $A^{1/3}$ with the isospin correction applied.}
\label{fig:IsoPlot}
\end{figure}

>>>>

\begin{figure}[p]
\centering
\includegraphics[width=7.4cm] {new-fig/40_Adep_Ratio_A13_0.png} 
\includegraphics[width=7.4cm] {new-fig/44_Adep_DePts_A13_0.png} 
\includegraphics[width=7.4cm] {new-fig/41_Ndep_Ratio_Nu_0.png} 
\includegraphics[width=7.4cm] {new-fig/46_Qdep_DePts_Q2_0.png} 
\includegraphics[width=7.4cm] {new-fig/42_zdep_Ratio_Zz_0.png} 
\includegraphics[width=7.4cm] {new-fig/47_zdep_DePts_Zz_0.png} 
\caption {Results for multiplicity ratios (left) and the transverse momentum 
broadening (right) before applying any corrections.}
\label{fig:prelim}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=7.4cm] {new-fig/50_Adep_Ratio_A13_1.png} 
\includegraphics[width=7.4cm] {new-fig/54_Adep_DePts_A13_1.png} 
\includegraphics[width=7.4cm] {new-fig/51_Ndep_Ratio_Nu_1.png} 
\includegraphics[width=7.4cm] {new-fig/56_Qdep_DePts_Q2_1.png} 
\includegraphics[width=7.4cm] {new-fig/52_zdep_Ratio_Zz_1.png} 
\includegraphics[width=7.4cm] {new-fig/57_zdep_DePts_Zz_1.png} 
\caption {Preliminary raw results are compared with the acceptance corrected ones, 
for multiplicity ratios (left) and transverse momentum broadening 
(right). Only statistical errors are shown.}
\label{fig:AcceptPlots}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=7.4cm] {new-fig/50_Adep_Ratio_A13_2.png} 
\includegraphics[width=7.4cm] {new-fig/54_Adep_DePts_A13_2.png} 
\includegraphics[width=7.4cm] {new-fig/51_Ndep_Ratio_Nu_2.png} 
\includegraphics[width=7.4cm] {new-fig/56_Qdep_DePts_Q2_2.png} 
\includegraphics[width=7.4cm] {new-fig/52_zdep_Ratio_Zz_2.png} 
\includegraphics[width=7.4cm] {new-fig/57_zdep_DePts_Zz_2.png} 
\caption {Preliminary results are compared with with and without Coulomb correction,
the acceptance remains applied for both. The multiplicity ratios are presented on the left 
and the transverse momentum broadening on the right. Only statistical errors are shown.}
\label{fig:CCPlots}
\end{figure}

@@

\begin{figure}[p]
\centering
\includegraphics[width=7.4cm] {new-fig/60_Adep_Ratio_A13_3.png} 
\includegraphics[width=7.4cm] {new-fig/64_Adep_DePts_A13_3.png} 
\includegraphics[width=7.4cm] {new-fig/61_Ndep_Ratio_Nu_3.png} 
\includegraphics[width=7.4cm] {new-fig/66_Qdep_DePts_Q2_3.png} 
\includegraphics[width=7.4cm] {new-fig/62_zdep_Ratio_Zz_3.png} 
\includegraphics[width=7.4cm] {new-fig/67_zdep_DePts_Zz_3.png} 
\caption {Preliminary results including radiative corrections
compared to the ones without (acceptance and Coulomb corrections remain applied in both), 
for multiplicity ratios (left) and transverse momentum broadening 
(right). Only statistical errors are shown.}
\label{fig:RCPlots}
\end{figure}

@@

\begin{figure}[tbp]
\centering
\includegraphics[width=8.5cm] {new-fig/IsospinCorrection.png}
\caption {Multiplicity ratios as a function of $A^{1/3}$ with and without the isospin correction applied.}
\label{fig:IsoPlot}
\end{figure}
